\UseRawInputEncoding
\documentclass[12pt]{article}
\title{ECE C143A Homework 6}
\usepackage{subcaption}
\author{Lawrence Liu}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage[scr]{rsfso}

\newcommand{\Laplace}{\mathscr{L}}
\setlength{\parskip}{\baselineskip}%
\setlength{\parindent}{0pt}%
\usepackage{xcolor}
\usepackage{listings}
\definecolor{backcolour}{rgb}{0.95,0.95,0.92}
\usepackage{amssymb}
\lstdefinestyle{mystyle}{
    backgroundcolor=\color{backcolour}}
\lstset{style=mystyle}

\begin{document}
\maketitle
\section*{Problem 1}
\subsection*{(a)}
False, the number of neurons in a brain is around 100x$10^9$ not $10^{12}$.
\subsection*{(b)}
False, the frontal lobe is in the front of the brain and the occipital lobe is in the back. 
\subsection*{(c)}
True
\subsection*{(d)}
False, "Each hemisphere is concerned primarily with sensory and motor processing of the contralateral (opposite) side of the body."
\subsection*{(e)}
True
\subsection*{(f)}
False, astrocytes form the blood brain barrier not the myelin sheets, the myelin sheets are created by Oligodendrocytes.
\subsection*{(g)}
True
\subsection*{(h)}
False,  neurons transmit information at the synapse chemically.

\subsection*{(i)}
False, Action potentials are “all or nothing” therefore the amplitude does not matter
\subsection*{(j)}
False they are more 10x more concentrated on the extracellular side.

\subsection*{(k)}
False, neurons fire at around 200Hz
\subsection*{(l)}
False, it is an increase
\subsection*{(m)}
True
\subsection*{(n)}
True
\subsection*{(o)}
False it will increase action potential speed.
\subsection*{(p)}
True
\subsection*{(q)}
True
\subsection*{(r)}
True
\subsection*{(s)}
True
\subsection*{(t)}
False, Anionic proteins residing in the cytoplasm are not as permeable to the membrane as sodium
and potassium ions.
\section*{Problem 2}
\subsection*{(a)}
$$E_K=\frac{58mV}{1}\log\frac{42}{336}=-52.379mV$$
$$E_{NA}=\frac{58mV}{1}\log\frac{300}{50}=45.132mV$$
\subsection*{(b)}
I would tell her to remeasure her results, because from Goldman's equation we would have that
$$V_m=\frac{RT}{F}\log\left(\frac{P_K[K^+]_o +P_{NA}[NA^+]_o+P_{CL}[CL^+]_o}{P_K[K^+]_i +P_{NA}[NA^+]_i+P_{CL}[CL^+]_i}\right)$$
Since the membrane is only permeable to Sodium and Potassium we have

$$V_m=58mV\log\left(\frac{[K^+]_o +\alpha[NA^+]_o}{[K^+]_i +\alpha[NA^+]_i}\right)$$

Where $\alpha=\frac{P_{NA}}{P_K}$. Thus $V_m$ has a minimum at $E_K=-52.379mV$ when $\alpha=0$ and a maximum $E_{NA}=45.132mV$ when $\alpha=\infty$. Therefore there is no way for $V_m=110mV$
\subsection*{(c)}
A higher value because that would result in a greater $E_NA$ and thus a greater maximum for $V_m$.
\section*{Problem 3}
\subsection*{(a)}
$$g_K=\frac{I_K}{(V_m-E_k)}=\frac{1pA}{45mV}=22.222pS$$
$$g_{NA}=\frac{I_{NA}}{(V_m-E_{NA})}=\frac{1pA}{50mV}=20 pS$$
\subsection*{(b)}
$$g_{IN}=g_K+g_{NA}$$
$$R_{IN}=\frac{1}{g_{IN}}=23.684 G\Omega$$
\subsection*{(c)}
$$C=\epsilon_0\frac{A}{d}=\epsilon_0\frac{4(10\mu m)^2 \pi}{100pm}=111.265pF$$
\subsection*{(d)}
The time constant for this Alien neuron is
$$\tau=R_{IN}C=2.635s$$
So this Alien lower will fire much more slowly than a human neuron
\section*{Problem 4}
\subsection*{(a)}
No they don't need to be equal and opposite, outside forces, such as the electrical fields caused by the flow of other ions.
\subsection*{(b)}
Through NA+-K+ pump.

\section*{Problem 5}
\subsection*{(a)}
we have
$$r_a=\frac{\rho}{\pi r^2}$$

$$c_m=\frac{\epsilon A}{d}$$
and that the action potential speed $\propto\frac{1}{r_ac_m}$


For species A we have
$$r_a=\frac{\rho}{\pi r^2}=\frac{\rho}{\pi (490\mu m)^2}$$
$$c_m=\frac{\epsilon \pi(490\mu m)^2}{10\mu m}$$Therefore the action potential speed for species A $\propto\frac{490\mu m}{\epsilon \rho}$\\\\
For species B we have
$$r_a=\frac{\rho}{\pi r^2}=\frac{\rho}{\pi (250\mu m)^2}$$
$$c_m=\frac{\epsilon \pi(250\mu m)^2}{250\mu m}$$
Therefore the action potential speed for species B $\propto\frac{250\mu m}{\epsilon \rho}$

Therefore species B would transmit faster.
\subsection*{(b)}
Yes, since the neurons take up the same space, but they they transmit faster, since the contribution from the area in $r_m$ and $c_m$ will cancel out.

\subsection*{(c)}
Nodes of Ranvier, are bare patches in a myelinated axon that that are densely populated with voltage-gated Na+ channels. These help boost the amplitude of a action potential so it doesn't die out.



 
\end{document}